--- 
title: "A series of R tutorials for teaching at the University of Oslo"
date: "`r Sys.Date()`"
author: "Even Sletteng Garvang"
site: bookdown::bookdown_site
documentclass: book
link-citations: yes
description: "This is a set of R tutorials written throughout the years teaching at UiO. These will hopefully give you a solid foundation for using R for coursework and master's theses"
---

# Preface {-}



```{r setup, include=FALSE}
source("setup.R")
library(tidyverse)
```

```{r html-doc, child="html_doc.Rmd", echo = FALSE}
```

## How to use these tutorials {-}

To get the most out of these tutorials, you should run all the provided code in R on your own computer while going through them. Rather than just copy/pasting all the code, we encourage you to write the code in manually. A great way to force yourself to do this is by changing some object names along the way. We also highly encourage you to experiment with the provided code. Please do change function arguments, values etc. to see what happens. If you ever think: "what happens if I...", try it! The worst thing that can happen is that you get an error.

During the tutorials, there are small exercises that we recommend that you do for your own understanding. Each tutorial also have assignments tied to what you have learned. If you are following the course BIOS1140 at UiO, be sure to deliver these assignments before the deadline. See the [appendix](#rmarkdown) for how you should deliver the assignments.

We use colour-coded boxes in the tutorials to summarise information and give additional tips.  The colors are explained below.

::: {.green}
**Important concept:**\
*Green boxes summarises important concepts from the text.*
:::

::: {.blue}
**Additional info**\
*Blue boxes contain small tips and additional information for those that are interested. What's in these is hopefully useful, but not mandatory. Feel free to skip these if you want.*
:::


**Text in bold contains small exercises to do on your own throughout the tutorials.**
